% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[a4paper,11pt]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Akhil S. Behl}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics, machine learning, big data},
  pdftitle = {Resume: \name},
  pdfsubject = {Resume},
  pdfpagemode = UseNone
}

\geometry{
  body={6in, 9in},
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Format abbreviations
\newcommand{\abbrv}[1]{\textsc{#1}}

% Make lists without bullets
\renewenvironment{itemize}{
\begin{list}{}{
  \setlength{\leftmargin}{1.5em}
  }
  }{
\end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  A13, Sai Shakti, Sai Baba Complex \\
  Mohan Gokhale Road, Goregaon East \\
  Mumbai (400 065), \abbrv{mh, india} \\
\end{minipage}
\hspace*{0.8in}
\begin{minipage}{0.45\linewidth}
  \vspace*{-\baselineskip}
  \begin{tabular}{ll}
    Phone: & \tt +91 77 388 03 588 \\
    Email: & \href{mailto:akhilsbehl@gmail.com}{\tt akhilsbehl@gmail.com} \\
    Homepage: & \href{http://akhilsbehl.github.io}{\tt akhilsbehl.github.io} \\
  \end{tabular}
\end{minipage}

\section*{Objective}
Affiliate with a data science unit with a mandate of creating intellectual
property and products using rigorous research and best practices.

\section*{Work Experience}
\small{
\begin{itemize}
  \item \textbf{Lead Data Scientist}, June 2015 - Present \\
    \href{http://niffler.in}{Niffler Labs}, Mumbai
    \begin{itemize}
      \item Architected a NoSQL database for responses generated from the
        Niffler app. This included:
        \begin{enumerate}
            \item Setting up a replicated MongoDB production server on EC2
              instances.
            \item Automated downloading of data stream from Amazon S3 to
              database server using Amazon Simple Notification Service.
            \item Schematization of the responses data using a custom Python
              parser.
        \end{enumerate}
      \item Authored a Python library to generate ad-hoc and templated reports
        on the app usage data.
      \item Designed Django backend models for Niffler's ecommerce module.
    \end{itemize}
    \vspace*{\baselineskip} %\\
  \item \textbf{Data Scientist} at Fractal Sciences, August 2013 - Present \\
    \href{http://fractalanalytics.com}{Fractal Analytics}, Mumbai
    \begin{itemize}
      \item Developed text classification infrastructure in Python (text
        processing) \& R (machine classification) to mine probability of
        successful subrogation from field notes of agents for a global
        insurance giant. Exceeded client benchmark of 80\% accuracy.
        \emph{Highlights}: SVM
        (\href{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}{libsvm} \&
        \href{http://www.csie.ntu.edu.tw/~cjlin/liblinear/}{liblinear}),
        sparse-matrix computation,
        \href{http://cran.r-project.org/web/packages/Rcpp/index.html}{RCPP}.
      \item Provided on-site consulting for predicting product supply Case Fill
        Rate for one of the biggest global CPG companies. \emph{Highlights}: 3+
        TB data, Hive, HadoopStreaming with R \& Python, Markov Chain analysis,
        Beta regression. (Retained as Technical Advisor for phase two of the
        project.)
      \item Retained as off-site Technical Advisor by the CPG client for
        forecasting success of retail initiatives. The Fractal team won the
        project against reputed international competitors. \emph{Highlights}:
        TBs of POS data; Hive optimizations.
      \item Co-developed a generic text-categorization algorithm and
        independently programmed this as a Python package.
      \item Protoyped and successfully marketed a fuzzy string matching
        solution in Python to standardize transaction merchant names for a
        major customer loyalty management firm.
      \item Project manager and data scientist for a web application to design
        and evaluate experiments in retail and CPG. Researched and programmed
        the \href{www.hks.harvard.edu/fs/aabadie/ccsp.pdf}{synthetic control}
        technique for the statistical kernel of the app.
      \item Official R trainer for Fractal Analytics Academy: trained more than
        75 new joinees.
      \item Attended \href{http://university.cloudera.com/course/developer}
        {Cloudera's developer training for Apache Hadoop}.
    \end{itemize}
    \vspace*{\baselineskip} %\\
  \item \textbf{Research Associate}, September 2012 - July 2013 \\
    \href{http://ifrogs.org}{Finance Research Group},
    \href{http://www.igidr.ac.in}{IGIDR}, Mumbai
    \begin{itemize}
      \item Co-authored a
        \href{http://ifrogs.org/releases/Thomasetal2013_systemicRisk.html}{policy
        paper} on identification of Indian firms contributing to systemic risk
        in the financial markets.
      \item Co-author of a statistical package
        \href{https://r-forge.r-project.org/projects/ifrogs/}{\emph{ifrogs}}
        for the \href{http://www.r-project.org}{R statistical language}.
      \item Presented an R implementation of the Model Confidence Set
        econometric technique at the
        \href{https://www.rmetrics.org/meielisalp2012}{6th RMetrics Conference
        at ETH Zurich}.
      \item Co-designer, developer, and maintainer of a tick-level
        financial research database comprised of data from the National
        Stock Exchange, India, and other sources.
      \item Implemented a program to validate daily NSE tick-level data on
        Trades and Orders in C \& Python. The framework has now been adopted by
        the NSE for integration with their IT system.
    \end{itemize}
    \vspace*{\baselineskip} %\\
  \item \textbf{Consultant Analyst}, June 2010 - January 2011 \\
    \href{http://www.cirm.in/} {Centre for Insurance \& Risk Management},
    IFMR Research, Chennai
    \begin{itemize}
      \item Co-authored a
        \href{http://www.munichre-foundation.org/dms/MRS/Documents/Microinsurance/2010_IMC/S11_MIC2010_Presentation_Behl.pdf}{paper}
        on design of experiments to assess impact of health micro insurance on
        low-income households.
      \item Developed statistical analysis modules and reports focusing on
        mining trend anomalies for
        \href{http://www.rsby.gov.in/}{Rashtriya Swasthya Bima Yojana},
        a pan-India state-sponsored third party payment health
        insurance scheme.
      \item Presented the paper and analysis mentioned above at the 6th
        International Micro Insurance Conference, Manila, Phillipinnes.
      \item Successfully completed \emph{Performance Consulting Skills}
        training by Nigel Harrison of
        \href{http://performconsult.co.uk/}{Performance Consulting}, UK.
      \item Research lead for two projects. Responsibilities included managing
        collaborations with project implementation, academic research, and
        sponsor fund partners; managing contract services and field staff;
        research design and supervision; data procurement, management and
        analysis; publication and presentation of research.
    \end{itemize}
\end{itemize}}

\section*{Education}
\begin{itemize}
  \item \textbf{MSc Economics}, Class of 2010, IGIDR, Mumbai, CGPA: 3.14/4.00.
  \item \textbf{BSc Mathematics}, Class of 2008, Hansraj College, University of
    Delhi, Score: 66.67\%.
  \item \textbf{MPhil Economics}, August 2011 - September 2012, IGIDR, Mumbai
    (\emph{Discontinued}).
\end{itemize}

\section*{Skills}
\begin{itemize}
  \item \textbf{Professional:}
    Proficiency in verbal and written business communication; experience with
    client and partner interaction; experience with technical consulting;
    comfortable with both team work and leadership; organized, methodical and
    punctual.
  \item \textbf{Technical:}
    \begin{itemize}
      \item \emph{Statistical analyses}: exploratory data analysis; sampling;
        hypothesis testing \& inference; regression analysis; univariate time
        series analysis; monte carlo simulations; bootstrap simulations; design
        of experiments.
      \item \emph{Machine learning}: Supervised: logistic regression, CART,
        random forests, gradient boosting machines, support vector machines;
        Unsupervised: k-means clustering; Recommender systems: collaborative
        filtering; Text mining: categorization; classification; fuzzy matching,
        Evaluation methods: k-fold cross validation, LOOCV, cost-based
        learning.
      \item \emph{Mathematical}: modeling; optimization; real analysis; graph
        theory; game theory.
    \end{itemize}
  \item \textbf{Personal:}
    Self-driven and motivated; challenge seeking; hard-working; patient;
    comfortable with different cultures and personalities.
\end{itemize}

\section*{Computation}
\begin{itemize}
  \item \textbf{Programming Languages}: R (advanced); Python (advanced); C
    (intermediate); BASH scripting (advanced); Common Lisp (intermediate).
  \item \textbf{Big Data Technologies}: Cloudera Hadoop; Hive; HadoopStreaming.
  \item \textbf{Miscellaneous}: MySQL (intermediate), MongoDB (intermediate);
    Django web framework (intermediate).
  \item \textbf{Office Suites}: MS Office; LibreOffice; OpenOffice; \LaTeX{}.
  \item \textbf{Operating Systems}: Linux; MS Windows.
\end{itemize}

\end{document}
